### 2016-02-04 mcmc.tex
problems

@@

\begin{problem}
Look up the Rosenbrock density used as the demonstration case for the
\project{emcee} sampler (see \citealt{emcee}).
Tune up a M--H MCMC sampler to sample this density (this isn't trivial),
or just install and use \project{emcee} to sample it.
Now plot the $x$ and $y$ histograms of a 10,000-point sampling of this
distribution (you might have to sample more than 10,000 and thin the
chain), and also plot the two-dimensional scatter plot of $x,y$
samples.
Overplot on all three plots an indicator of the means and medians of
the samples along the $x$ and $y$ directions.
Overplot on all three plots the (above) recommended quantiles of the
samples.
Comment on the results.
\end{problem}

>>>>

\begin{problem}\label{prob:rosenbrock}
Look up the Rosenbrock density used as the demonstration case for the
\project{emcee} sampler (see \citealt{emcee}).
Tune the Gaussian proposal distribution in your M--H MCMC sampler to sample this density efficiently.
What autocorrelation time do you get?
Compare to what \project{emcee} gets.
\end{problem}

@@

\begin{problem}
Execute \problemname~\ref{prob:rosenbrock}, or, if you are lazy,
or just install and use \project{emcee} to do the hard work.
Now plot the $x$ and $y$ histograms of a 10,000-point sampling of this
distribution (you might have to sample more than 10,000 and thin the
chain), and also plot the two-dimensional scatter plot of $x,y$
samples.
Overplot on all three plots an indicator of the means and medians of
the samples along the $x$ and $y$ directions.
Overplot on all three plots the (above) recommended quantiles of the
samples.
Comment on the results.
\end{problem}
